--- 
title: "An Overview of AnVILBulkRNASeq"
author:
- name: Kayla Interdonato
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r Sys.Date()`"
output: 
    BiocStyle::html_document:
        toc: true
        toc_float: true
vignette: >
  %\VignetteIndexEntry{A_Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The goal of the `AnVILBulkRNASeq` package is to provide users all the tools to
perform a typical `DESeq2` analysis utilizing AnVIL. This package contains all
files (except for raw FASTQ files) needed to complete the analysis.

# Installation

The following code will install the latest version of `AnVILBulkRNASeq` package
from Bioconductor.

```{r install, eval = FALSE}
if(!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("AnVILBulkRNASeq")
```

The development version is also available for install from GitHub:

```{r github, eval = FALSE}
BiocManager::install("Kayla-Morrell/AnVILBulkRNASeq")
```

Then to load `AnVILBulkRNASeq`:

```{r load, message = FALSE}
library(AnVILBulkRNASeq)
```

# Overview

There are vignettes contained in the package that will explain each step as well
as provide code to be performed along the way. 

* *A_Overview*: An overview of what will be accomplished in this workspace.
* *B_OrganizingData*: Downloading an example dataset and where to store it.
* *C_RunningTheWorkflow*: How to run the AnVILBulkRNASeq workflow on example data.
* *D_ManagingTheWorkflowOutput*: Obtaining the output from the workflow.
* *E_DESeq2Analysis*: Analyzing and visualizing the workflow output data.
* *F_DataCleanUp*: Once data is in the workspace, how to clean up any unwanted data.

Each of the above vignettes corresponds to a Jupyter notebook in the
Bioconductor-Workflow-DESeq2 workspace on AnVIL. The code will be executable
whether running from the notebooks on the workspace or running locally from the
vignettes.

# Session Information

```{r}
sessionInfo()
```
