--- title: "An Overview of AnVILBulkRNASeq"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A_Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnVILBulkRNASeq)
```

# Introduction

The goal of this package is to provide users all the tools to perform a typical
`DESeq2` analysis utilizing AnVIL. The `AnVILBulkRNASeq` package contains all
files (except for raw FASTQ files) needed to complete the analysis. 

# Installation

```{r}
if(!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("AnVILBulkRNASeq")
```

# Overview

There are vignettes contained in this package that will explain each step as
well as code to be performed along the way. 

* A_Overview: An overview of what will be accomplished in this workspace.
* B_OrganizingData: Downloading an example dataset and where to store it.
* C_RunningTheWorkflow: How to run the AnVILBulkRNASeq workflow on example data.
* D_ManagingTheWorkflowOutput: Obtaining the output from the workflow.
* E_DESeq2Analysis: Analyzing and visualizing the workflow output data.

Each of the above vignettes corresponds to a Jupyter notebook in the
Bioconductor-Workflow-DESeq2 workspace on AnVIL. The code will be executable
whether running from the notebooks on the workspace or running locally from the
vignettes.

# Session Information

```{r}
sessionInfo()
```
