---
title: "A_Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A_Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnVILBulkRNASeq)
```

# Overview

The goal of this workflow is to demonstrate to the user how to utilize AnVIL for 
a typical `DESeq2` analysis. First, FASTQ files will be obtained from an online 
resource and quantified using Salmon. This quantification will be done through 
the AnVILBulkRNASeq workflow in the DESeq2 workspace on AnVIL. The output from 
the quantification will then be analyzed with `DESeq2`. This analysis is already 
planned out in the vignette for the package. All steps, along with any 
intermediate ones, will be outlined in various Jupyter notebooks located in 
the DESeq2 workspace. The following are the notebooks that are provided:

* A_Overview: An overview of what will be accomplished in this workspace.
* B_OrganizingData: Downloading an example dataset and where to store it.
* C_RunningTheWorkflow: How to run the AnVILBulkRNASeq workflow on example data.
* D_ManagingTheWorkflowOutput: Obtaining the output from the workflow.
* E_DESeq2Analysis: Analyzing and visualizing the workflow output data.
