---
title: "Managing the Workflow Output"
author:
- name: Kayla Interdonato
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r Sys.Date()`"
output:
    BiocStyle::html_document:
        toc: true
        toc_float: true
vignette: >
  %\VignetteIndexEntry{D_ManagingWorkflowOutput}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

This vignette will walk through managing the output data from the workflow that
was run in the previous vignette [Running the Workflow Within
AnVIL](C_RunningTheWorkflow.html).

# Installation

How to install the `AnVILBulkRNASeq` package is show in the first vignette [An
Overview of AnVILBulkRNASeq](A_Overview.html). Refer to that vignette for
installation steps. The following command will load the package.

```{r setup}
library(AnVILBulkRNASeq)
```

We will need the `AnVIL` package again for certain functionality so we will
install and load it now.

```{r install}
pkgs = "Bioconductor/AnVIL"
BiocManager::install(pkgs)

suppressPackageStartupMessages({
    library(AnVIL)
})
```

# Obtain paths of output

In order to run the `DESeq2` analysis in the next vignette, we must locate the
data that was the output from the `AnVILBulkRNASeq` workflow. The following code
will utilize functions from the `AnVIL` package to return the output paths.

```{r paths}
gs_paths <- avworkflow_jobs() %>% 
    head(1) %>% 
    avworkflow_files() %>%
    filter(startsWith(.data$file, "DRR")) %>% 
    pull(path)
```

`avworkflow_jobs()` will locate the list of jobs run on the AnVIL workspace.
The last job is grabbed using `head(1)`, then the files associated with that job
are listed using `avworkflow_files()`. We know that our samples files all have
"DRR" in the names so we use `filter(startsWith(.data$file, "DRR"))` to filter
out the files that start with "DRR". Then we use `pull(path)` to pull out the
paths where the output data was saved on the Google bucket.

With these paths, we can then copy the output tarballs to the current workspace
and untar them. Again, we will utilize functionality from `AnVIL` to achieve
this.

```{r untar}
AnVIL::gsutil_cp(gs_paths, getwd())

file_list <- basename(gs_paths)
lapply(seq_along(lengths(file_list)), function(x) untar(file_list[x]))
```

Now we have files for each sample that contains the necessary output files to
perform the `DESeq2` analysis on.

# Session Information

```{r, eval = TRUE}
sessionInfo()
```
