---
title: "Managing the Workflow Output"
author:
- name: Kayla Interdonato
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r Sys.Date()`"
output:
    BiocStyle::html_document:
        toc: true
        toc_float: true
vignette: >
  %\VignetteIndexEntry{D_ManagingWorkflowOutput}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

This vignette will walk through managing the output data from the workflow that
was run in the previous vignette [Running the Workflow Within
AnVIL](C_RunningTheWorkflow.html).

# Installation

How to install the `AnVILBulkRNASeq` package is show in the first vignette [An
Overview of AnVILBulkRNASeq](A_Overview.html). Refer to that vignette for
installation steps. The following command will load the package.

```{r setup}
library(AnVILBulkRNASeq)
```
