---
title: "Cleaning up Data on the AnVIL Workspace"
author:
- name: Kayla Interdonato
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r Sys.Date()`"
output:
    BiocStyle::html_document:
        toc: true
        toc_float: true
vignette: >
  %\VignetteIndexEntry{F_DataCleanUp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction 

This vignette will explain some of the ways you can clean up data in an AnVIL
workspace from your local computer. This vignette will use many functions from
the Bioconductort `r Biocpkg("AnVIL")`. In order for these commands to work
locally we assume that gcloud SDK is installed. If you need help with this,
please refer to the `AnVIL` package vignette for installation steps.

# Installation

The first vignette [An Overview of AnVILBulkRNASeq](A_Overview.html) shows how
to install the `AnVILBulkRNASeq` package. Refer back to vignette if package is
not installed. The following command will load the package.

```{r setup}
library(AnVILBulkRNASeq)
```

The vignette [Running the Workflow Within AnVIL](C_RunningTheWorkflow.html)
explains how to install the `AnVIL` package. If you need help installing, please
refer to that vignette. We will now load the `AnVIL` package.

```{r anvil}
pkgs = c("Bioconductor/AnVIL", "dplyr")
BiocManager::install(pkgs)

suppressPackageStartupMessages({
    library(AnVIL)
    library(dplyr)
})
```

# Setting up the workspace

The first step is to make sure that the proper workspace is being used. We
define our workspace using the `avworkspace` function.

```{r workspace}
avworkspace("bioconductor-rpci-anvil/Bioconductor-Workflow-DESeq2")
avworkspace_namespace()
avworkspace_name()
```

# Cleaning up data 

There may be times where incorrect data is saved in the tables, tables are made
in error, or data sets need to be deleted / created. We will walk through each
of these scenarios below and how you can rectify them using functions from
`AnVIL`.

## Deleting information from a table

While creating our `participant` table, an entry was added in error as well as
some extra columns. We tried to create the proper table and import it using
`avtable_import()` but the incorrect entry was never deleted. `AnVIL` has a
function `avtable_delete_values()` that will help get rid of any unnecessary
entries. We will demonstrate this function below.

```{r grab_table}
avtables()
tbl <- avtable("participant")
```

First we can filter out the extra columns `fastq1` and `fastq2` since we were
looking for `fastq_1` and `fastq_2`.

```{r filter_columns}
tbl <- tbl %>% filter(!is.na(files)) %>% select(-c("fastq1", "fastq2"))
```

It's important to note that when we ran `avtable` the first column got renamed
to `name` and we need it to be `participant` or else when we import it a table
`name` will be created.

```{r rename}
tbl <- tbl %>% rename(participant = "name")
```

Now that we have the proper columns we can delete the unneeded entry
'DRR015126' and import the clean table.

```{r delete_values}
avtable_delete_values("participant", "DRR015126")
avtable_import(tbl)
```

It's important to note that if the value being deleted is in any other tables or
sets, the value will not be deleted. In our examples, 'DRR015126' was in some
sets so the sets had to be deleted (since they were not needed) and then the
single entry in the `participant` table could be deleted. See further section on
how to delete entire sets.

## Deleting tables

When working with the workflow, a `name` table was made in error (due to the
fact that `avtable()` renames the `participant` column to `name`). We want to
delete any unnecessary tables so there are only tables that we need in the
workspace. The following will demonstrate how to delete entire tables.

We will take the `name` table, pull out all the name values from it, and delete
them from the table. An empty table will not show in the AnVIL workspace.

```{r delete_table}
value <- avtable("name") %>% pull(name)
avtable_delete_values("name", value)
```

## Working with sets

We will first demonstrate how to delete entire sets from the workspace. This is
done in a similar manner as when deleting values from a table.

```{r delete_sets}
avtable_delete_values("participant_set", "salmon_quant_2020-09-23T12-45-29")
```

Instead of providing the table name and value to be deleted, to delete a set you
must provide the set name and the set id that should be deleted.

Now to create a set you must use the `avtable_import_set` function. We will
create a `participant_set` using the participants from the `participant` table.
This set is what will be used when running the `AnVILBulkRNASeq` workflow.

```{r import_set}
avtable("participant") %>% 
    mutate(set = "participant_set") %>% 
    avtable_import_set("participant", "set", "name")
```

# Session Information

```{r, eval = TRUE}
sessionInfo()
```
